---
title: "Rmarkdown_notes"
author: "Korin Eckstrom"
output: html_document


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
```


## Analysis of Life Expectancy by Continent
Hypothesize taht life expectancy is a function of location and XX

[Link to github repo](https://github.com/keckstrom/2019-04-02-carpentries-mmc)


```{r, echo=FALSE, message=FALSE}
#Read in the data
d <- readr::read_csv(here("data/gapminder/raw/gapminder_data.csv"))

d %>%
  filter(continent == "Africa") %>%
  ggplot( aes(x= year, y= lifeExp)) + 
  geom_line() + facet_wrap(~country)

#population over time
ggplot(data = filter(d, continent == "Asia")) + geom_line(aes(x= year, y= pop,
                            group=country, color = country))


```


## Details
The data consists of years from `r range(d$year)`.


# this will automatically update the report from the dataset in the document
# may need to use round if you aren't working with year (i.e. how many digits to print)

```{}

```

